---
title: "Country level visualisation for Mainland China"
author: "Ernest Guevarra"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Country level visualisation for Mainland China}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  message = FALSE,
  warning = FALSE,
  error = FALSE,
  collapse = TRUE,
  comment = "#>"
)
```

In this vignette, we show how to perform the OxCOVID19 Database visualisation examples shown [here](https://github.com/covid19db/examples/blob/master/data-plots/confirmed-adm-1-level-china.ipynb) using R and the `oxcovid19` package.

## Retrieving epidemiology data for single source

```{r example1, echo = TRUE, eval = TRUE}
library(oxcovid19)
library(magrittr)
library(dplyr)

connect_oxcovid19() %>%
  get_table(tbl_name = "epidemiology") %>%
  filter(source == "CHN_ICL",
         !is.na(adm_area_1)) %>%
  arrange(desc(date))
```

## Extracting only recent data - total per region

```{r example2a, echo = TRUE, eval = TRUE}
chn_recent_region <- connect_oxcovid19() %>%
  get_table(tbl_name = "epidemiology") %>%
  filter(source == "CHN_ICL",
         !is.na(adm_area_1)) %>%
  group_by(adm_area_1) %>%
  filter(as.Date(date) == max(as.Date(date), na.rm = TRUE)) %>%
  select(date, country, adm_area_1, confirmed, recovered, dead, gid) %>%
  collect()
```

```{r example2b, echo = FALSE, eval = TRUE}
chn_recent_region
```

## Retrieving administrative division level 1 for single country

```{r example3a, echo = TRUE, eval = TRUE}
chn_admin_1 <- connect_oxcovid19() %>%
  get_layer(ccode = "CHN", adm = 1) %>%
  collect()
```

```{r example3b, echo = FALSE, eval = TRUE}
chn_admin_1
```

## Merge administrative division and epidemiology data

```{r example4a, echo = TRUE, eval = TRUE}
## Load sf package for spatial objects
library(sf)

chn_recent_region <- chn_recent_region %>%
  mutate(gid = as.character(stringr::str_remove_all(string = gid, 
                                                    pattern = "\\{|\\}"))) %>%
  left_join(y = chn_admin_1, by = "gid") %>%
  st_as_sf()
```

```{r example4b, echo = FALSE, eval = TRUE}
chn_recent_region
```

## Plot epidemiology total confirmed

```{r example5a, echo = TRUE, eval = TRUE}
plot(chn_recent_region["confirmed"], nbreaks = 10, breaks = "quantile")
```
